Group Fou\\*R* Term Project

### 2018-12-16 Draft.Rmd
.

---
title: "Group Fou\\*R* Term Project - Summary of Raw Data, Explanations and Preliminary Analysis"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
date: "December 2018"
output: html_document
---
## Explanatory Data Analysis of Trade Statistics of Turkey

@@

### Data Preparation, cleaning and Manipulation

@@

###Analysis

####SALIH

@@

@@

#Import percentage Values in $

pim_table<-vtable%>%filter(year=='2017')%>%
  mutate(perc_count=co_total/sum((vtable%>%filter(year=='2017'))$co_total)*100)%>%
  select(Country,year,co_total,perc_count)

ggplot(pim_table, aes(x="", y=perc_count, fill=Country)) + geom_bar(stat="identity", width=1)+
  coord_polar("y") + geom_text(aes(label = round(perc_count,1), "%"), position = position_stack(vjust = 0.5))+
  labs(x = NULL, y = NULL, fill = NULL, title = "Percentage of Countries in Import in 2017")+theme_classic()+
  theme(axis.text = element_blank(),plot.title = element_text(hjust = 0.5, color = "#666666"))

####OMER

In order to deeply understand the data; we build up shiny app with Country, Product and Year variables.

@@

####MUHARREM
####Analysis of Trade Deficit by Countries and Years

# Total Net Value fiiled with Country on the basis of Year #
ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
  labs(subtitle="## Total Net Value fiiled with Country on the basis of Year ##", title= "Total Net Values") + 
  coord_flip()+
  theme(legend.position = "top")
```

IMAGE

###OMER2

####EMRE

####Analysis of Year by Year Change in Trade Values

@@

plotCanEx <- ggplot(summarytableCanadaEx, aes(x=substr(X__2, start = 1, stop = 30))) +
  geom_point(aes(y=ExpChngYoy, color=year), size=4) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid (~year) +
  facet_grid(rows = vars(year)) +
  labs(title="YoY Total Value Change with Canada - Export",
       x="Product Group",
       y="Change in Export Value",
       Color=c("Year"))

@@

@@

>>>>

---
title: "Group Fou\\*R* Term Project"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
date: "December 2018"
output: html_document
---
## Explanatory Data Analysis of Trade Statistics of Turkey

@@

### Data Preparation, Cleaning and Manipulation

@@

### Analysis

#### Breakdown of Total Export and Import of Turkey Over Countries

@@

At import side, Turkeys' biggest trade partners are China, Germany, Russia and US while they are Germany, UK, Italy and USA at export side. Germany and USA are the 2 countries exist for both type of trade.

When we breakdown this info to years:

@@

Except Russia, fluctuates over years are not seem so significant.

In order to deeply understand the data; we build up shiny app with Country, Product and Year variables to review export and import values.

@@

##### YORUM VE IMAGE EKLENECEK

#### Analysis of Year by Year Change in Trade Values

@@

plotCanEx <- ggplot(summarytableCanadaEx, aes(x=substr(X__2, start = 1, stop = 30))) +
  geom_point(aes(y=ExpChngYoy, color=year), size=4) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid (~year) +
  facet_grid(rows = vars(year)) +
  labs(title="YoY Total Value Change with Canada - Export",
       x="Product Group",
       y="Change in Export Value",
       Color=c("Year"))
```

```{r, echo=FALSE}
# Import Analysis

@@

```{r, echo=FALSE}

@@

#### Analysis of Trade Deficit by Countries and Years

# Total Net Value fiiled with Country on the basis of Year #
ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
  labs(subtitle="Total Net Value fiiled with Country on the basis of Year ##", title= "Total Net Values") + 
  coord_flip()+
  theme(legend.position = "top")
```

##### IMAGE EKLENECEK

#### Correlation of Trade Deficit with FX Rate and BIST100 index
